Modelling palaeoecological time series using generalized additive models

### 2018-06-25 manuscript.Rmd
fix figure 14 so it actually uses half a column for panel a

plot_grid(plt1, plt2, plt3, ncol = 1, labels = "auto", align = "hv", axis = "lrtb",
          rel_widths = c(0.5, 1, 1))
```

>>>>

## align all plots vertically
plots <- align_plots(plt1, plt2, plt3, align = 'v', axis = 'l')

## create the two rows of figures, from `plots`
top_row <- plot_grid(plots[[1]], NULL, ncol = 2, labels = "a")
bot_row <- plot_grid(plots[[2]], plots[[3]], ncol = 1, labels = c("b", "c"))

## combine the two rows, top row has 1 row of plots, bottom row has 2, hence
## the rel_heights to even this out
plot_grid(top_row, bot_row, ncol = 1, rel_heights = c(0.5, 1))
```
